Universal Anonymous Signatures

### 2022-06-07 prism-backend/research/gsac/app-building-blocks.tex
Updated sign-unforgeability proof.

\paragraph{Augmenting with NIZKs.} %
\todo{This is quite informal. Perhaps expand...} 
In the previous \SBCM scheme, it is straightforward to require that the party
running \SBCMCom proves some arbitrary claim over the messages to be signed
(both those in committed or plaintext form). This can be done by having this
party add a NIZK over the corresponding NP statement. We will be using this
extension, and use $\SBCM^{\NIZKRel}$ to denote such an \SBCM with proofs for
claims in \NIZKRel.

>>>>

\paragraph{Augmenting with NIZKs.} %
\todo{This is quite informal. Perhaps expand...} 
In the previous \SBCM scheme, it is straightforward to require that the party
running \SBCMCom proves some arbitrary claim over the messages to be signed
(both those in committed or plaintext form). This can be done by having this
party add a NIZK over the corresponding NP statement, which has later to be
verified by the party running \SBCMSign. We will be using this extension, and
use $\SBCM^{\NIZKRel}$ to denote such an \SBCM with proofs for claims in
\NIZKRel.

### 2022-06-07 prism-backend/research/gsac/app-gsac.tex
Quick full pass (excl. appendices).
Minor edits and fixing typos.
Updated sign-unforgeability proof.

        \procedure{$\CHALb(\ccid_0,\ccid_1,\dattrs,\msg)$}{%
          \pcif \dattrs \nsubseteq \ATTR[\ccid_0] \cap \ATTR[\ccid_1]:
          \pcreturn \bot \\
          \pcif \cuid_0 \neq \bot \lor \cuid_1 \neq \bot: \pcreturn \bot \\
          \cuid_0 = \OWNR[\ccid_0];~\cuid_1 = \OWNR[\ccid_1] \\
          \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
 %         \pcif \ccid_0 \in \CCRED \lor \ccid_1 \in \CCRED: \pcreturn \bot \\
          \csig \gets \Sign(\gpk,\PRVUK[\cuid_b],\CRED[\ccid_b],
          \dattrs,\msg) \\
          \CSIG \gets \CSIG \cup \lbrace \csig \rbrace \\
          \pcreturn \csig
        }

@@

\subsection{Detailed Proofs}
\label{sapp:gsac-proofs}

@@

  We begin with game $G_0=\ExpGSACAnonb$. From it, we build $G_1$, where we
  simply replace the \NIZKSetup functions for $\NIZKRel_{\Sign}$ and
  $\NIZKRel_{\Open}$ within the \Setup algorithm. $G_1$ is indistinguishable
  from $G_0$ due to the zero-knowledge property of the NIZK systems.

@@

  Now, observe that in $G_2$, the challenge signature received by the adversary
  is completely independent from the challenge bit $b$. Moreover, as argued,
  $G_2$ is indistinguishable from $G_0$, where the adversary plays the original
  \ExpGSACAnonb game. Thus, our generic construction of \GSAC satisfies
  anonymity, except with negligible probability.
  %
  \qed
\end{proof}

@@

\paragraph{Anonymity.} To see why the interactive variant is anonymous, assume
an adversary $\adv$ against anonymity in that case. We build \advB against the
non-interactive \ExpGSACAnonb as follows. \advB initializes everything as in the
\ExpGSACAnonb game. When $\adv$ initiates a call to its interactive \SIGN (resp.
\CHALb) oracle, \advB picks a random number, and sends it to the adversary,
along with the response of its own (non-interactive) \SIGN (resp. \CHALb)
oracle where, to the message passed as parameter to its oracle, concatenates the
produced random number. After such simulation, \advB just outputs whatever
$\adv$ outputs. Clearly, the simulation is perfect and, if $\adv$ wins with
non-negligible probability in the interactive case, then so does \advB in the
non-interactive case.

>>>>

        \procedure{$\CHALb(\ccid_0,\ccid_1,\dattrs,\msg)$}{%
          \pcif \dattrs \nsubseteq \ATTR[\ccid_0] \cap \ATTR[\ccid_1]:
          \pcreturn \bot \\
          \cuid_0 = \OWNR[\ccid_0];~\cuid_1 = \OWNR[\ccid_1] \\
          \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
 %         \pcif \ccid_0 \in \CCRED \lor \ccid_1 \in \CCRED: \pcreturn \bot \\
          \csig \gets \Sign(\gpk,\PRVUK[\cuid_b],\CRED[\ccid_b],
          \dattrs,\msg) \\
          \CSIG \gets \CSIG \cup \lbrace \csig \rbrace \\
          \pcreturn \csig
        }

@@

\subsection{Correctness and Security Proofs}
\label{sapp:gsac-proofs}

@@

  We begin with game $G_0=\ExpGSACSigAnonb$. From it, we build $G_1$, where we
  simply replace the \NIZKSetup functions for $\NIZKRel_{\Sign}$ and
  $\NIZKRel_{\Open}$ within the \Setup algorithm. $G_1$ is indistinguishable
  from $G_0$ due to the zero-knowledge property of the NIZK systems.

@@

  Now, observe that in $G_2$, the challenge signature received by the adversary
  is completely independent from the challenge bit $b$. Moreover, as argued,
  $G_2$ is indistinguishable from $G_0$, where the adversary plays the original
  \ExpGSACSigAnonb game. Thus, our generic construction of \GSAC satisfies
  anonymity, except with negligible probability.
  %
  \qed
\end{proof}

@@

\paragraph{Issuance Anonymity.} \todo{XXX}

\paragraph{Signature Anonymity.} To see why the interactive variant is
anonymous, assume an adversary $\adv$ against anonymity in that case. We build
\advB against the non-interactive \ExpGSACSigAnonb as follows. \advB initializes
everything as in the \ExpGSACSigAnonb game. When $\adv$ initiates a call to its
interactive \SIGN (resp. \CHALb) oracle, \advB picks a random number, and sends
it to the adversary, along with the response of its own (non-interactive) \SIGN
(resp. \CHALb) oracle where, to the message passed as parameter to its oracle,
concatenates the produced random number. After such simulation, \advB just
outputs whatever $\adv$ outputs. Clearly, the simulation is perfect and, if
$\adv$ wins with non-negligible probability in the interactive case, then so
does \advB in the non-interactive case.

### 2022-06-07 prism-backend/research/gsac/construction-uas.tex
Updated sign-unforgeability proof.

\begin{description}
\item[$\NIZKRel_{\Issue}$:] Set by issuers, governs via \fissue the rules for
  issuing new credentials. It is defined as $\NIZKRel_{\Issue} = \lbrace
  (\usk,\scred,\attrs_{\scred},r), (\Ccom,\attrs,\sipk_{\scred}): \Ccom =
  \CCommit(usk;r) \land \fissue(\usk,\scred,\attrs) = 1 \land \forall \cred \in
  \scred, \SBCMVerify(\ipk_{\cred},\cred,\usk,\attrs_{\cred}) = 1 \rbrace$,
  where for readability we write $\attrs_{\scred}$ as abbreviation for $\lbrace
  \attrs_{\cred} \rbrace_{\cred \in \scred}$, and similarly for $\sipk_{\scred}$.
  Basically, this relation requires that, in order to issue a credential with
  attribtes \attr, and bound to \usk, the requester has to commit to \usk and
  prove knowledge of it, as well as prove that all additional credentials needed
  for the issuing to be granted, meet some defined policy \fissue.
\item[$\NIZKRel_{\Sign}$:] Can be set by anyone but, for simplicity, assume
  verifiers define them. Governs via \feval and \finsp what utility
  information is directly revealed by signatures, or extracted by openers.
  It is defined as $\NIZKRel_{\Sign} = \lbrace (\usk,\scred,
  \attrs_{\scred},\yeval^1,\yinsp,r,r'),(\msg,\feval,\yeval^0,\ceval,\cinsp,
  \sipk_{\scred},\Eek): \ceval = \EEnc(\Eek,\yeval^1;r) \land \cinsp= \EEnc
  (\Eek,\yinsp;r') \land (\yeval^0,\yeval^1) = \feval(\usk,\scred,\msg) \land
  \yinsp = \finsp((\yeval^0,\yeval^1),\usk,\scred,\msg) \land \forall \cred \in
  \scred, \SBCMVerify(\ipk_{\cred},\cred,\usk,\attrs_{\cred}) = 1) \rbrace$,
  with $\attrs_{\scred}$ and $\sipk_{\scred}$ as in $\NIZKRel_{\Issue}$. In a
  nutshell, this relation ensures that signatures will produce the correct
  signature evaluation and opening values, and that any credential used to
  create the signature is bound to the same \usk key.
\item[$\NIZKRel_{\Open}$:] Ensures that the utility information extracted by
  the \Open algorithm is correct. It is defined as $\NIZKRel_{\Open} =
  \lbrace (\osk),(\Ec,\yinsp): \yinsp = \EDec(\osk,\Ec) \rbrace$.
\end{description}

@@

\paragraph{$\Sig \gets \Sign(\usk,\opk,\scred,\msg,\feval)$.} %
In the signing algorithm, we make use of relation $\NIZKRel_{\Sign}$.
% 
From this, in order to produce a valid signature, the user first evaluates
$(\yeval^0,\yeval^1) \gets \feval (\usk,\scred,\msg)$, and decides whether or
not to continue with the signing process -- this may depend, e.g., on the
opening policy of \opk, as the output of \feval may influence whether the user
will be de-anonymizable or not, depending on the \finsp function in \opk.
%
Then, the user parses \opk as $(\Svk,\Eek,\finsp,\sig_{\finsp})$ and checks that
$\Verify(\Svk,\sig_{\finsp},\finsp) = 1$ (note that this step may be cached), to
compute $\yinsp \gets \finsp((\yeval^0,\yeval^1),\usk,\scred,\msg)$, and
separately encrypts both $\yeval^1$ and \yinsp with \Eek by running
$\ceval \gets \EEnc(\Eek,\yeval^1;r)$ and $\cinsp \gets \EEnc(\Eek,\yeval^1;
r')$ for some fresh randomness $r,r'$. Finally, the user computes
$\NIZKproof \gets \NIZKProve^{\NIZKRel_{\Sign}}(\NIZKcrs_{\Sign},(\usk,\scred,
\attrs_{\scred},\yeval^1,\yinsp,r),(\msg,\feval,\yeval^0,\ceval,\cinsp,
\sipk_{\scred},\Eek))$ and outputs $(\sig = (\NIZKproof,\cinsp),\yeval,
\ceval)$.

@@

\paragraph{$1/0 \gets \Judge(\opk,\yinsp,\NIZKproof,\sig,\yeval,\msg)$.} %
To assess the validity of an opening proof, first check the signature
by running $\Verify(\opk,\sipk, \sig,\yeval,\msg,\feval)$. If the check succeeds,
parse \sig as $((\cdot,\cinsp),\cdot)$ and verify \NIZKproof with $\NIZKVerify
(\NIZKcrs_{\Open},\NIZKproof,(\cinsp,\yinsp))$. Accept it the NIZK
verification passes, and reject otherwise.

>>>>

\begin{description}
\item[$\NIZKRel_{\Issue}$:] Set by issuers, governs via \fissue the rules for
  issuing new credentials. It is defined as $\NIZKRel_{\Issue} = \lbrace
  (\usk,\scred,\attrs_{\scred},r), (\Ccom,\attrs,\sipk_{\scred}): \Ccom =
  \CCommit(usk;r) \land \fissue(\usk,\scred,\attrs) = 1 \land \forall \cred \in
  \scred, \SBCMVerify(\ipk_{\cred},\cred,\usk,\attrs_{\cred}) = 1 \rbrace$,
  where for readability we write $\attrs_{\scred}$ as abbreviation for $\lbrace
  \attrs_{\cred} \rbrace_{\cred \in \scred}$, and similarly for $\sipk_{\scred}$.
  Basically, this relation requires that, in order to issue a credential with
  attribtes \attr, and bound to \usk, the requester has to commit to \usk and
  prove knowledge of it, as well as prove that all additional credentials needed
  for the issuing to be granted, meet some defined policy \fissue.
\item[$\NIZKRel_{\Sign}$:] Can be set by anyone but, for simplicity, assume
  verifiers define them. Governs via \feval and \finsp what utility
  information is directly revealed by signatures, or extracted by openers.
  It is defined as $\NIZKRel_{\Sign} = \lbrace (\usk,\scred,
  \attrs_{\scred},\yeval^1,\yinsp,r,r'),(\msg,\feval,\yeval^0,\ceval,\cinsp,
  \sipk_{\scred},\Eek,\widetilde{\Eek}): \ceval = \EEnc(\widetilde{\Eek},\yeval^1;r)
  \land \cinsp= \EEnc (\Eek,\yinsp;r') \land (\yeval^0,\yeval^1) = \feval(\usk,
  \scred,\msg) \land \yinsp = \finsp((\yeval^0,\yeval^1),\usk,\scred,\msg) \land
  \forall \cred \in \scred, \SBCMVerify(\ipk_{\cred},\cred,\usk,\attrs_{\cred})
  = 1) \rbrace$, with $\attrs_{\scred}$ and $\sipk_{\scred}$ as in
  $\NIZKRel_{\Issue}$. In a
  nutshell, this relation ensures that signatures will produce the correct
  signature evaluation and opening values, and that any credential used to
  create the signature is bound to the same \usk key.
\item[$\NIZKRel_{\Open}$:] Ensures that the utility information extracted by
  the \Open algorithm is correct. It is defined as $\NIZKRel_{\Open} =
  \lbrace (\osk),(\Ec,\yinsp): \yinsp = \EDec(\osk,\Ec) \rbrace$.
\end{description}

@@

\paragraph{$\Sig \gets \Sign(\usk,\opk,\scred,\msg,\feval)$.} %
In the signing algorithm, we make use of relation $\NIZKRel_{\Sign}$.
% 
From this, in order to produce a valid signature, the user first evaluates
$(\yeval^0,\yeval^1) \gets \feval (\usk,\scred,\msg)$, and decides whether or
not to continue with the signing process -- this may depend, e.g., on the
opening policy of \opk, as the output of \feval may influence whether the user
will be de-anonymizable or not, depending on the \finsp function in \opk.
%
The user also computes a random encryption key pair with $(\widetilde{\Eek},
\widetilde{\Edk}) \gets \EKeyGen(\Eparm)$. Then, the user parses \opk as $(\Svk,\Eek,
\finsp,\sig_{\finsp})$ and checks that $\Verify(\Svk,\sig_{\finsp},\finsp) = 1$
(note that this step may be cached), to compute $\yinsp \gets \finsp((\yeval^0,
\yeval^1),\usk,\scred,\msg)$, and separately encrypts both $\yeval^1$ and
\yinsp by running $\ceval \gets \EEnc(\widetilde{\Eek},\yeval^1;r)$ and $\cinsp \gets
\EEnc(\Eek,\yinsp; r')$ for some fresh randomness $r,r'$. Finally, the user
computes $\NIZKproof \gets \NIZKProve^{\NIZKRel_{\Sign}}(\NIZKcrs_{\Sign},(\usk,
\scred, \attrs_{\scred},\yeval^1,\yinsp,r,r'),(\msg,\feval,\yeval^0,\ceval,\cinsp,
\sipk_{\scred},\Eek,\widetilde{\Eek}))$ and outputs $(\sig = (\NIZKproof,\ceval,
\cinsp),\yeval^0)$.

@@

\paragraph{$1/0 \gets \Judge(\opk,\yinsp,\NIZKproof,\Sig,\msg)$.} %
To assess the validity of an opening proof, first check the signature
by running $\Verify(\opk,\sipk,\Sig,\msg,\feval)$. If the check succeeds,
parse \Sig as $((\cdot,\cinsp),\cdot,\cdot)$ and verify \NIZKproof with
$\NIZKVerify(\NIZKcrs_{\Open},\NIZKproof,(\cinsp,\yinsp))$. Accept it the NIZK
verification passes, and reject otherwise.

### 2022-06-07 prism-backend/research/gsac/model-gsac.tex
Updated sign-unforgeability proof.

\begin{figure}[htp!]
  \procedure[linenumbering]{$\ExpGSACAnonb(1^\secpar)$}{%
     \parm \gets \Setup(1^\secpar) \\
     (\ipk,\isk) \gets \IKeyGen(\parm);~(\opk,\osk) \gets \OKeyGen(\parm);~ 
     \gpk \gets (\ipk,\opk) \\
     b^* \gets
     \adv^{\HUGEN,\CUGEN,\WREG,\OBTAIN,\SIGN,\OPEN,\CHALb}(\gpk,\isk,\status) \\
     \pcreturn b^*
  }
  \caption{Anonymity experiment for \GSAC schemes.}
  \label{fig:exp-gsac-anonb}
\end{figure}

\begin{definition}{(Anonymity of \GSAC)}
  \label{def:anonymity-gsac}
  We define the advantage \AdvGSACAnon of $\adv$ against \ExpGSACAnonb as
  $\AdvGSACAnon=|\Pr\lbrack\ExpGSACAnono(1^\secpar)=1\rbrack-
  \Pr\lbrack\ExpGSACAnonz(1^\secpar)=1\rbrack|$.
  %
  A \GSAC scheme satisfies anonymity if, for any p.p.t. adversary $\adv$,
  \AdvAnon is a negligible function of $1^\secpar$.
\end{definition}

>>>>

\begin{figure}[htp!]
  \procedure[linenumbering]{$\ExpGSACSigAnonb(1^\secpar)$}{%
    \parm \gets \Setup(1^\secpar) \\
    (\ipk,\isk) \gets \IKeyGen(\parm);~(\opk,\osk) \gets \OKeyGen(\parm);~ 
    \gpk \gets (\ipk,\opk) \\
    b^* \gets
    \adv^{\HUGEN,\CUGEN,\WREG,\OBTAIN,\SIGN,\OPEN,\OBTCHALb}(\gpk,\isk,\status) \\
    \pcreturn b^*
  }

  \vspace*{0.5em}

  \procedure[linenumbering]{$\ExpGSACSigAnonb(1^\secpar)$}{%
    \parm \gets \Setup(1^\secpar) \\
    (\ipk,\isk) \gets \IKeyGen(\parm);~(\opk,\osk) \gets \OKeyGen(\parm);~ 
    \gpk \gets (\ipk,\opk) \\
    b^* \gets
    \adv^{\HUGEN,\CUGEN,\WREG,\OBTAIN,\SIGN,\OPEN,\CHALb}(\gpk,\isk,\status) \\
    \pcreturn b^*
  }
  \caption{Issuance and signature anonymity experiments for \GSAC schemes.}
  \label{fig:exp-gsac-anonb}
\end{figure}

\begin{definition}{(Issuance anonymity of \GSAC)}
  \label{def:iss-anonymity-gsac}
  We define the advantage \AdvGSACIssAnon of $\adv$ against \ExpGSACIssAnonb as
  $\AdvGSACIssAnon=|\Pr\lbrack\ExpGSACIssAnono(1^\secpar)=1\rbrack-
  \Pr\lbrack\ExpGSACIssAnonz(1^\secpar)=1\rbrack|$.
  %
  A \GSAC scheme satisfies issuance anonymity if, for any p.p.t. adversary
  $\adv$, \AdvGSACIssAnon is a negligible function of $1^\secpar$.
\end{definition}

\begin{definition}{(Signature anonymity of \GSAC)}
  \label{def:sig-anonymity-gsac}
  We define the advantage \AdvGSACSigAnon of $\adv$ against \ExpGSACSigAnonb as
  $\AdvGSACSigAnon=|\Pr\lbrack\ExpGSACSigAnono(1^\secpar)=1\rbrack-
  \Pr\lbrack\ExpGSACSigAnonz(1^\secpar)=1\rbrack|$.
  %
  A \GSAC scheme satisfies signature anonymity if, for any p.p.t. adversary
  $\adv$, \AdvGSACSigAnon is a negligible function of $1^\secpar$.
\end{definition}
